### 2021-03-05 introduction.tex
set up the contributions of the paper

We presented and evaluated DroidXP in a conference paper~\cite{DBLP:conf/scam/CostaMCMVBC20},
and here we discuss the results of a broader investigation
that also uses DroidXP to explains the performance of static and dynamic analysis
approaches for mining sandboxes.

%Altogether, this paper brings the following contributions:
\todo[inline]{RB.: Later we can enumerate the paper contributions here.}

\todo[inline]{RB: review the following paragraph later}
The rest of the paper is organized as follows. Section 2 we present a background and some related works. Section 3 introduces the study setting of our research and Section 4 complements presenting some results and discussion, highlighting motivation malware examples and the use of a promising static analysis tool, on these examples. Finally, Sections 5 and 6, summarizes the paper, presenting some threats, presenting the final conclusions, and discussing our ideas for future works.

>>>>

We presented and evaluated DroidXP in a conference paper~\cite{DBLP:conf/scam/CostaMCMVBC20},
and here we discuss the results of a broader investigation
that also uses DroidXP to explains the performance of static and dynamic analysis
approaches for mining sandboxes. Altogether, this paper brings the following contributions:

\begin{itemize}
\item A replication of the \blls study that better clarifies the performance of
  dynamic analysis tools for mining Android sandboxes.

\item A broad comprehension about the role of static analysis tools for mining
  sandboxes, showing that we can benefit from using both static and dynamic
  analysis for detecting Android malwares.

\item Evidence that a well known static analysis approach, based on
  taint analysis, leads to a performance similar to the dynamic analysis
  approach for mining sandboxes.

\item A replication package of our study that is available on-line, including
  scripts for statistic analysis \footnote{https://htmlpreview.github.io/?https://github.com/droidxp/paper-replication-package/blob/master/replication.html}
  and a benchmark for reproducing and extending our study.\footnote{https://github.com/droidxp/benchmark} 
\end{itemize}

%% \todo[inline]{RB: review the following paragraph later}
%% The rest of the paper is organized as follows. Section 2 we present a background and some related works. Section 3 introduces the study setting of our research and Section 4 complements presenting some results and discussion, highlighting motivation malware examples and the use of a promising static analysis tool, on these examples. Finally, Sections 5 and 6, summarizes the paper, presenting some threats, presenting the final conclusions, and discussing our ideas for future works.
